### 2017-06-27 2017/NACO/paper.tex

$\varphi(y^l(x))$, $1 \leq l \leq s$ obtained as a result of the dimensionality

@@

      in accordance with the set of mappings \(y^l(x), 1\le l\le s\) for each problem from the family (\ref{eq:oneDimProblemSerie}),
      \item send the prototypes \(x_i',1\leq i\leq s\) to all computational nodes in order

@@

      \item to send the prototypes \(x_i',1\leq i\leq s\) and the result of the trial

>>>>

$\varphi(y^l(x))$, $1 \leq l \leq s$, obtained as a result of the dimensionality

@@

      in accordance with the set of mappings \(y^l(x), 1\le l\le s\), for each problem from the family (\ref{eq:oneDimProblemSerie}),
      \item send the prototypes \(x_i',1\leq i\leq s\), to all computational nodes in order

@@

      \item to send the prototypes \(x_i',1\leq i\leq s\), and the result of the trial
